### 2014-05-07 acks.tex
Add Pratiksha

Many others helped to develop the ideas in this work, especially Chris
Amato, Andrew McGregor, Tim Shepard, John Wroclawski, Bill McCloskey, Josh Mandel,
Carrie Niziolek, Damon Wischik, Hariharan Rahul, Chris Lesniewski,
Vikash Mansinghka, Eric Jonas, Marissa Cheng, and Allie Brownell.

>>>>

Many others helped to develop the ideas in this work, especially
Pratiksha Thaker, Chris Amato, Andrew McGregor, Tim Shepard, John
Wroclawski, Bill McCloskey, Josh Mandel, Carrie Niziolek, Damon
Wischik, Hariharan Rahul, Chris Lesniewski, Vikash Mansinghka, Eric
Jonas, Marissa Cheng, and Allie Brownell.
